### 2016-06-28 testbed.tex
..

We proceed to define the testbed environment by each of its conforming
parts. We later indicate a procedure to set up the testbed. In this procedure,
we summarize all the details regarding on setting the connectivity and
system files for a set of \ac{Raspi}s in a decentralized fashion.
Afterwards, we indicate how to cross-compile C++ code and the Kodo
network coding library in an easy way.
%Finally, we provide further information about Kodo itself in terms
%of testing, other platforms supported and source code documentation
%for further references.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.85\textwidth]{images/testbed_setup2.eps}
\caption{Testbed setup}
\label{fig:testbed_setup}
\end{figure}

%This section will present a testbed of thirty \ac{Raspi}s and a \ac{PC}
The testbed consists of thirty \ac{Raspi}s that will be setup and controlled
by a testbed administrator from a \ac{PC}.
%Twenty \ac{Raspi} 1 model B revision 2 and ten \ac{Raspi} 2 model B V1.1.
The \ac{Raspi}s are each equipped with a memory card and a wired and wireless
network interface. They are all connected to the
university network by wire using their ethernet interface (eth0).

To easily discover the \ac{Raspi}s within the university network,
%by a testbed administrator from a \ac{PC}. The \ac{Raspi}s are each equipped
%with a memory card and connected to the
%university network by wire using their ethernet interface (eth0). To easily
%discover the \ac{Raspi}s within the university network,
they have all been assigned a unique name under a common domain.
This eliminates the need to remember their individual \ac{IP} addresses.
A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.
We have two types of \ac{Raspi}s in our setup.
Table~\ref{tab:rasp_naming} shows the naming convention.

\begin{table}[ht!]
  \centering
  \begin{tabular}{|c|c|}
    \hline
      \textbf{Hostname} & \textbf{Model} \\ \hline
    rasp00 - rasp19 & Raspberry Pi 1 model B rev. 2 \\ \hline
    rasp20 - rasp29 & Rasperry Pi 2 model B V1.1 \\ \hline
  \end{tabular}
  \caption{Raspberry Pi naming convention}
  \label{tab:rasp_naming}
\end{table}

%Accessing them is easily done using \ac{SSH}.
%To address them within the university network,
%The \ac{Raspi}s

%The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
%connected by wire to the university's \ac{LAN}. The university network
%administration was provided
%the \ac{MAC} addresses of the ethernet interfaces to automatically assign
%the devices the desired \ac{IP} addresses as shown in the figure. In a personal
%\ac{LAN}, another option could be to manually provide the devices with static
%\ac{IP}s.

%This section will be used to present a \ac{Raspi} testbed and the steps to
%install and configure its devices.

%The testbed is depicted in figure~\ref{fig:testbed_setup}. It consists of twenty
%Raspberry Pi 1 model B rev 2 (Rasp01 to Rasp20) and
%ten Raspberry Pi 2 model b V1.1 (Rasp2\_01 to Rasp2\_10).

The testbed is available for students to perform simulations and
measurements as part of their semester projects. The \ac{Raspi}s should
be configured identically, but allow the students to alter the
configurations and how each \ac{Raspi} behaves.
%It is therefore desired
%that the \ac{Raspi}s are configured identically, but still allows the
%students to alter the configurations.

When working on a testbed with many devices, it is not always desired
to make persistent
changes to devices. We present how the concept of stacked
filesystems is used to enable the means of both persistent and
%The testbed should be usable by students to perform simulations and
%measurements as part of their semester projects. It is therefore desired
%that the \ac{Raspi}s are configured identically, but still allows the
%students to alter the configurations. When working on a testbed, it is
%not always desired to make persistent
%changes to the devices. We also present how the concept of stacked
%filesystems can be used to enable the means of both persistent and
temporary storage.

%It is therefore
%mandatory that the \ac{Raspi}s are easily configurable but also
%desired to

%The testbed should be usable by students that should be able to configure
%the \ac{Raspi}'s as desired. It is therefore

%The testbed will be used by students that might need to change how the
%devices are work either temporary or permanently. We will illustrate how this
%can be accomplished using an overlaying filesystem.

%The goal is to configure all the \ac{Raspi}s identically with the same software
%and configurations. There are however a few differences between them that we
%need to take into account. E.g. hostname and network addresses.

%Finally, it should be possible to store data that are generated from
%simulations on the memory cards that are in the individual \ac{Raspi}.
%We using a overlaying filesystem that
%We will illustrate
%how that can be done. In the case of temporary changes, it is important that
%all changes can be easily reverted. We put a \ac{RAM} filesystem on top of
%the the root filesystem to .
%the configure the
%devices to behave according to their test specifications. We
%will also present how that might be done.

%their linkings. That could be to change network config

%The goal is to configure all the devices to be as identical as possible. This
%means that it is desired to have the same software on every device, but

%The \ac{Raspi}s are all equipped with an ethernet interface (eth0) and
%connected by wire to the university's \ac{LAN}. The university network
%administration was provided
%the \ac{MAC} addresses of the ethernet interfaces to automatically assign
%the devices the desired \ac{IP} addresses as shown in the figure. In a personal
%\ac{LAN}, another option could be to manually provide the devices with static
%\ac{IP}s.
%that are
%assigned the \ac{IP} addresses in the figure and connected wired to the
%university's \ac{LAN}.

%We use standard usb power adapters to power the \ac{Raspi}s.

@@

We will be using a \ac{PC} running a Debian-based Linux distribution
%\ac{Raspi}s. We will use Raspbian Linux~\cite{raspbian}. We will be
%using a \ac{PC} running a Debian-based Linux distribution
to setup a customized Raspbian Linux image that can be written to
a memory card and work in any \ac{Raspi} version 1 or 2.
%We will use a desktop that has linux installed to download,
%configure, and write the image to the memory cards.
%We have decided to use a linux desktop machine to create a
%common image of Raspbian Linux that can be used in any of the Raspberry Pis.

%for all devices. After the image has been configured it can be written to
%a memory card and used in any of the Raspberry Pis. This means that each
%device needs a memory card, but it does not matter which card is put into
%which device.

%We have decided to go with Raspbian linux~\cite{raspbian} and
%to install it on memory cards.

%There exists a number of ways to setup a testbed in a centralized manner.
%E.g. using e.g. \ac{NFS}.

%There exists a number of ways to setup a testbed
%
%with multiple devices. We
%have decided on a very simple approach of simply instal

%-
%- Download image (wget)
%- Update/Modify image (chroot)
%- Burn image
%- Bang! linux is running
%-

%Open a terminal, and then...

%The first thing we need to do is to download the linux installation file.
%For Raspbian, this is available at \url{http://downloads.raspberrypi.org}.

@@

Below is the procedure we followed to setup the \ac{Raspi}s in our testbed. We
%connect to another machine through a command shell. In fact it is the successor
%of \ac{Telnet} that has been designed with network security in mind.
%
%Our testbed does not have monitors so we will install Raspbian lite.
%A desktop environment can be installed using Raspbian's package manager
%(apt-get) in case a desktop environment will be desired sometime in the future.
%Below is the procedure we did to setup the \ac{Raspi}s in our testbed. We
have performed a simple setup where each \ac{Raspi} is equipped with a
memory card that contains a slightly customized Raspbian lite image. The image
of the \ac{OS} in all \ac{Raspi}s will be identical.
%with identical settings.

%The reason this can be done easily is because the official Raspbian lite image
%that we will download simply conntains a complete linux installation that are
%packaged in an image rather than written to a harddrive, memory card, or usb
%pen.

@@

Hashmark (\#) and dollar (\$) will be used throughout the code blocks in
the paper to indicate if an operation needs to be run with root permissions or
user permissions.
%In the following, the hashmark (\#) and dollar (\$) signs will be used
%throughout the procedure to indicate if an operation should be run with
%root permissions or user permissions.
%\textbf{hashmark (\#) means to perform operation as root, dollar (\$) means
%to perform operation as user}

@@

It is seen that the image is now available as /dev/loop0. Use \texttt{lsblk}
to view the partitions:

>>>>

We proceed to define the testbed environment by each of its conforming
parts. We later indicate a procedure to set up the testbed. In this procedure,
we summarize all the details regarding on setting the connectivity and
system files for a set of \ac{Raspi}s in a decentralized and/or centralized fashion
depending on the testbed admins preferences..
%Afterwards, we indicate how to cross-compile C++ code and the Kodo
%network coding library in an easy way.
%Finally, we provide further information about Kodo itself in terms
%of testing, other platforms supported and source code documentation
%for further references.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{images/testbed_setup3.eps}
\caption{Testbed setup}
\label{fig:testbed_setup}
\end{figure}

The testbed consists of up to one hundred \ac{Raspi}s of different models.
More specifically, Raspberry Pi 1 model B rev.~2,
Raspberry Pi 2 model B V1.1, and Raspberry Pi 3 model B V1.2.
All \ac{Raspi}s are each equipped with a memory card, a wired, and a wireless
network interface. They connect to the university network using its wired
ethernet interface that is named \texttt{eth0} according to the legacy naming
convention of ethernet interfaces in Linux. \textcolor{red}{MAYBE PUT SOUECE HERE}

All \ac{Raspi}s will be running an \ac{SSH} daemon for easy remote access
within the university network. We therefore had the university's \ac{IT}
department configure the university's \ac{DHCP} server to assign each \ac{Raspi} a
static \ac{IP}. This eliminates the requirements for monitors and keyboards
for the \ac{Raspi}s for non-graphical applications.
%This significantly eases the management of the \ac{Raspi}s
%as \ac{SSH} eliminates the need for monitors and keyboards for the \ac{Raspi}s.

A sketch of the testbed is depicted in Figure~\ref{fig:testbed_setup}.

The testbed should be available for students to perform simulations and
measurements as part of their semester projects. We intend to configure
all \ac{Raspi}s identically, while still allowing students to alter
how each \ac{Raspi} behaves and is configured.

When working on the testbed with this many devices, it may not always be
desired to make persistent changes to devices. We present how the concept
of stacked filesystems may be used to enable the means of both persistent
and temporary storage.

%The testbed should be available for students to perform simulations and
%measurements as part of their semester projects. The \ac{Raspi}s should
%be configured identically, but allows the students to alter the
%configurations and how each \ac{Raspi} behaves.
%
%When working on a testbed with many devices, it may not always desired
%to make persistent changes to devices. We present how the concept of stacked
%filesystems may be used to enable the means of both persistent and
%temporary storage.

%A \ac{HTTP} server will be used to store Linux configuration files as well
%as the root filesystem in the centralized approach.

The following procedure will explain how the testbed may be setup and
configured both in the traditional distributed fasion where the
entire Linux filesystem is written to an memory card, but also in a more
centralized fasion where 
is written to
Based on the popular Debian based Raspbian Linux distribution
We
first present how a standard Linux distribution for the \ac{Raspi}s
may be customized

@@

We will be using a \ac{PC} running a Debian-based Linux distribution
to setup a customized Raspbian Linux image that can be written to
a memory card and work in any \ac{Raspi} version 1 or 2.

@@

Below is the procedure we followed to setup the \ac{Raspi}s in our testbed. We
have performed a simple setup where each \ac{Raspi} is equipped with a
memory card that contains a slightly customized Raspbian lite image. The image
of the \ac{OS} in all \ac{Raspi}s will be identical.

@@

Hashmark (\#) and dollar (\$) will be used throughout the code blocks in
the paper to indicate if an operation needs to be run with root permissions or
user permissions.

@@

It is seen that the image is now available as \texttt{/dev/loop0}. Use \texttt{lsblk}
to view the partitions:
